\begin{rubric}{Awards \& Funding}
\entry*[12/2025]%
	\textbf{Best Poster Award}
    \par German Autonomy Summit, Munich (Germany), 2025 ($3^{\mathrm{rd}}$ place).

\entry*[12/2025]%
	\textbf{Humboldt Post-doctoral Fellowship} 
    \par $2$-year funding for post-doctoral researchers, following the evaluation of a research proposal (\textbf{success rate $<20$\%}).

\entry*[10/2025]%
	\textbf{Best Workshop Paper Award} 
		\par 2025 IEEE IROS conference, Workshop on Planning, Perception and Navigation for Intelligent Vehicles.

\entry*[09/2025]%
	\textbf{Best Ph.D. Thesis Award} 
		\par Issued by the journal \textit{MDPI Vehicles}.

\entry*[08/2025]%
	\textbf{IEEE ITSS Best Dissertation Award} 
    \par Issued by the IEEE Intelligent Transportation Systems Society.

\entry*[08/2025]%
	\textbf{IEEE IES-SYPA Travel Award} 
    \par Issued by the IEEE Industrial Electronics Society (IES) for participation in the 2025 IEEE IROS conference (\textbf{success rate $<10$\%}).

\entry*[06/2025]%
	\textbf{Best Paper Award Finalist} 
		\par 2025 IEEE Intelligent Vehicles (IV) Symposium.

\entry*[03/2025]%
	\textbf{EuroTech Visiting Researcher Award} 
    \par $15$-day research travel grant to collaborate with the Eindhoven University of Technology, following a competitive selection of a research proposal.
    
\entry*[12/2024]%
	\textbf{TUM Global Post-doctoral Fellowship} 
    \par $2$-year funding for early-career researchers, following the evaluation of a research proposal ($10$ funded positions,
		\textbf{success rate $<10$\%}).

\entry*[07/2024]%
	\textbf{IFAC Young Author Award} 
    \par Awarded at the $17^{\mathrm{th}}$ IFAC Symposium on Control in Transportation Systems, Cyprus.

\entry*[05/2024]%
	\textbf{Best Paper Award Finalist} 
    \par $10^{\mathrm{th}}$ International Conference on Vehicle Technology and Intelligent Transport Systems (VEHITS).

\entry*[04/2024]%
	\textbf{Ph.D. Graduation with Highest Distinction} (\textit{summa cum laude})

\entry*[11/2023]%
	\textbf{Best Poster Award}
    \par Industrial Engineering Day, University of Trento (Italy).

\entry*[10/2019]%
	\textbf{M.Sc. Graduation with Highest Distinction} (\textit{summa cum laude})

\entry*[09/2017]%
	\textbf{B.Sc. Graduation with Highest Distinction} (\textit{summa cum laude})

\end{rubric}
    