\begin{rubric}{Teaching and Supervision Experience}
%

\text{\par
    \vspace{-0.15cm}
    \begin{tabular}{|m{0.37\linewidth}|m{0.55\linewidth}|}
    \hline
    \textbf{Metric} & \textbf{Value} \\
    \hline
    N. courses taught (Master level) & $1$ (Univ. of Trento, Italy) + $3$ (TUM, Germany) \\\hline
    N. hours of lectures & $50$ (Univ. of Trento, Italy) + $15$ (TUM, Germany) \\\hline
    N. exam sessions prepared and corrected & $6$ (Univ. of Trento, Italy) + $4$ (TUM, Germany) \\\hline
    N. co-supervised Ph.D. students & $1$ (Univ. of Trento, Italy) + $5$ (TUM, Germany) \\\hline
    N. supervised visiting Ph.D. students & $3$ (TUM, Germany) \\\hline
    N. co-supervised Master students & $9$ (Univ. of Trento, Italy) + $7$ (TUM, Germany) + $1$ (HAN, The Netherlands) + $1$ (EIT Digital Master School, EU) \\\hline
    \end{tabular}\par
}
\subrubric{}
%
\entry*[07/2025 -- present]%
	\textbf{Teaching Assistant}, Technical University of Munich, Germany
    \par Master courses of: 
    \vspace{-0.3cm}
    \begin{itemize}
        \item \textit{Autonomous Vehicles: Motion Planning and Decision Making} \vspace{-0.35cm}
        \item \textit{Ethical Robot Systems} \vspace{-0.35cm}
        \item \textit{F$1$TENTH: Autonomous Driving Hands-on} 
    \end{itemize}\vspace{-0.1cm}
    \par Responsibilities:\vspace{-0.3cm}
    \begin{itemize}
        \item Preparation of slides and materials for selected lectures.\vspace{-0.35cm}
        \item Lecturer for selected lectures.\vspace{-0.35cm}
        \item Support with exam preparation and correction.
    \end{itemize}
%
\vspace{-0.1cm}
\entry*[\begin{tabular}{@{}r@{}}
        09/2021 -- 02/2022\\
        09/2020 -- 02/2021\\
        11/2019 -- 02/2020
        \end{tabular}]%
	\textbf{Teaching Assistant}, EIT Digital Master School, University of Trento, Italy
    \par Master course of \textit{Vehicle Dynamics, Planning and Control of Robotic Cars}.
    \vspace{-0.3cm}
    \begin{itemize}
        \item Preparation of lecture slides and assignments.\vspace{-0.35cm}
        \item Holding lectures and exercise sessions.\vspace{-0.35cm}
        \item Grading assignments and providing feedback to students.
    \end{itemize}
%
\entry*[03/2025 -- 03/2026]%
	\textbf{Program Assistant}, Robotics Institute Germany, Germany
    \par Assistance in the creation of a new Master of Science in AI-based Robotics across different universities in Germany.
    \vspace{-0.3cm}
    \begin{itemize}
        \item Definition of requirements from the industry and research community.\vspace{-0.32cm}
        \item Survey-based analysis of strengths and weaknesses of the current academic educational landscape in robotics.
    \end{itemize}
%
\entry*[2025 -- present]%
	\textbf{Thesis Co-Supervisor}, Technical University of Munich, Germany
    \vspace{-0.3cm}
    \begin{itemize}
        \item $5$ Ph.D. Students \vspace{-0.35cm}
        \item $7$ Master Students \vspace{-0.35cm}
        \item $3$ Visiting Ph.D. Students
    \end{itemize}
%
\entry*[2019 -- present]%
	\textbf{Thesis Co-Supervisor}, University of Trento, Italy
    \vspace{-0.3cm}
    \begin{itemize}
        \item $1$ Ph.D. Student \vspace{-0.35cm}
        \item $9$ Master Students
    \end{itemize}
%
\entry*[2021 -- 2022]%
	\textbf{Thesis Co-Supervisor}, EIT Digital Master School (EU)
    \vspace{-0.3cm}
    \begin{itemize}
        \item $1$ Master Student \vspace{-0.35cm}
        \item $1$ Term Project
    \end{itemize}
%
\entry*[2020 -- 2021]%
    \textbf{Thesis Co-Supervisor}, HAN University of Applied Sciences, Netherlands
    \vspace{-0.3cm}
    \begin{itemize}
        \item $1$ Master Student
    \end{itemize}
\end{rubric}
